% copyright page
\noindent{\footnotesize{The first two parts of the book are a work of fiction. The names of entities, such as characters and companies, portrayed in it are either the product of the author's imagination, or used in a fictitious manner. Any resemblance to actual persons, living or dead, or resemblance to the entities such as companies or brands, is entirely coincidental. The incidents described are based on real happenings, with a judicious amount of dramatization for the benefit of the reader, as well as minor inaccuracies owing to the limitations of the process of recollection/reproduction.

The non-fictitious information provided within this Book is for general informational purposes only. These opinions, calculations, and analyses are intended purely to communicate information in accordance with the right to freedom of speech and expression. The author is not a lawyer, and this work does not constitute legal advice. Readers are also advised to obey all applicable laws, express or implied, in their region. While all attempts have been made to keep the information up-to-date and correct, there are no representations or warranties, express or implied, about the completeness, accuracy, reliability, suitability or availability with respect to the information contained in this book, for any purpose. The author does not assume any responsibility for the consequences of anyone acting according to this information.

\vfill\noindent Paperback Edition\space\today\\\ccbyncsa\space\theauthor. Some rights reserved.

\noindent ISBN \isbn

\vfill\noindent Pyramid on My Roof by \href{https://www.amazon.com/author/ram.iyer}{Ram Iyer} is licensed under a \href{http://creativecommons.org/licenses/by-nc-sa/4.0/}{Creative Commons Attribution-NonCommercial-ShareAlike~4.0 International License}.}}

\clearpage
