# The Nexus

The illusion of the flickering lights calmed her nerves, while her lower abdomen agitated them. It was an uncomfortable feeling, a feeling that she'd endured for a long time now. It punctually came every month, as if it were a German train. She sat down, letting her legs hang off the parapet. She broke down, cried. She growled as the pain ripped her apart. All she had to do to end everything that was going on inside her, everything that was eating away at her, everything that was hurting her, was to push with her arms placed on the parapet. Four seconds, and it would all end. But somehow she felt she didn't want to take that plunge---yet.

She unlocked her cell phone, to go through a few messages for the last time---the messages that she cherished. She would then go over to the gallery and see some pictures. The long ride and Rasta Café were all she could think of. It was her birthday celebration---belated. She'd loved the night. She'd loved the company. It had been,arguably, the best night she'd had in the last twenty-seven years. It had been the two of them, riding on the NICE\ road, riding at 130 kilometres an hour, wind in her hair. He was the quintessential gentleman---her "Mr\ Goody Two-Shoes"; her "Chief". He did everything with a certain grace---starting from writing, to eating, to walking, he did everything just how it should be---not an inch here, not an inch there---quite like how he rode. He cherished everything that belonged to him, just like how he cared for his R15. Everything about him was clean, it all had that neatly-tended look. It reminded her of the garden back home in Coimbatore; how she admired it and loved to play there all her childhood! Then she thought about how she'd found it immensely cute, that her name was typically part of his: Frieda and Friedrich.

She thought about his innocent face, smiling at the camera with the boyish charm and the cheekiness of a fourteen-year-old. A side of her head wanted to pull up the image and kiss it on the five-inch screen of her beautiful Nexus\ 5---he'd bought her that for her birthday; the other side only reminded her of that kiss that had started this all, the kiss that had set the wheels rolling for this day to come. _That fateful kiss._

She could distinctly remember the day she sat next to him at the bar. It was funny how memory worked: the more you asked it to forget something, the deeper the incident got etched. They had spent quite some time chatting that evening. Even though they'd been almost neighbours, they'd not spoken much to each other in person. It had all been text. This felt nice, the physical presence. He was enjoying the buzz and along with the music, bobbing his head. Chuckling, she ran her fingers through his short hair. The head stopped bobbing, they looked into each other's eyes. They leant forward, closed their eyes and remained there, unsure whether to go further or not. Without them realising, their lips touched. The warmth filled them, and they let it take over. It was beautiful for the few seconds that it lasted. Unlike a cigarette butt that burnt you when it ended, this one had left them feeling amazing; complete. They actually felt good about this even though they were friends, and such a thing happening between friends was usually known to end badly. But then it was arguable that there was always an exception; why couldn't they be the exception? Or was all this the alcohol thinking?

She'd found the next morning beautiful. She was tired of the lonely life she'd thought she'd have. It had been all bright and beautiful; she was having the best time of her life. Romance is all about uncertainty, they say. And that uncertainty makes the adrenaline rush through the blood. It is an amazing feeling, they say. She'd felt all that. She'd had no idea what was going on in his head. But she'd trusted him. While she knew there was no way to surely tell if he meant the kiss as something meaningful, something told her he would come around, and very soon.

And very soon he did. He'd dropped her a message asking her if she'd like to join him for a drink. She had nothing better to do, and it was him who'd asked. She loved every minute she spent with him and didn't want to let go of the opportunity. He picked her up in an hour and they were on their way. The city looked beautiful from the pillion seat of his Yamaha, and every word he uttered was funny. They cracked her up. Was she in love? Was he too thinking what she was? A part of her wanted to know. She knew she could just ask him. He was the kind that handled everything with a smile and a shrug.

They sat drinking their beer when he said, 'Frieda, I'm not sure what I feel, but I think this is good, what we have.' She smiled. Her head was racing with all the thoughts she'd had before she'd gotten on that bike of his. They looked into each other's eyes and understood each other. Her happiness had known no bounds that evening. She was on cloud nine.
```{r echo=FALSE}
scenebreak()
```
They spent the nights talking about different things, about life, about love, about family... The only thing that bothered them was that she was Catholic and he was Jewish. They knew their parents wouldn't allow this. Being part of the Indian society meant that their parents' decision, likes and dislikes, mattered to them in a life-changing way. A sense of emptiness had started to engulf her now. He didn't seem to have enough courage to go talk to his parents about it, nor did she. Her mum would probably agree if she knew it was him whom she liked; her dad would lose it. The nights had become gloomy, partly because of the weather, and partly because of the darkness they were in.
```{r echo=FALSE}
scenebreak()
```
'So what do you think we should do', she'd asked. He'd just sent a sad smiley. They sat across the city---her in her room and him at the bar. He was sloshed, as was his Saturday ritual. Her room was dark; the door was closed. She sat in a corner, withdrawing herself so much that the room almost felt empty. She couldn't think of anyone else in her life, definitely not someone like her ex, Rod. After a while into their relationship, all that the guy had wanted was sex. And he'd tried to torture her to get it. Being a Catholic, she wasn't up for it. She believed it was a sin---that was what had been taught to her since she was a child. She'd ended it right there; she was scared of such guys now. She wanted someone like Fred, and she knew that guys his kind were hard to find. She didn't want to lose him, and she would go miles if she had to, if that could get her what she wanted.

However, that night, while texting, one thing had led to another, and they'd ended up sending a lot of content: text as well as multimedia. The next morning had welcomed her with a blanket each of guilt and self-loathing covering her face, not allowing her to breathe. She'd cried, cried herself out over the thought of exchanging so much over the phone. But something inside her told her it was OK, that she could trust him.

He'd come to console her later that morning while there was nobody else at home. The feelings had resurfaced, and they'd then gotten lost in each other.
